The Unified Nature of the Dielectric Properties of Two-Dimensional Materials

### 2018-11-12 paper.tex
Shorten the introduction part from Elton

The central place of dielectric properties, especially the static
dielectric constant in material research
\cite{Dressel_2001_electrodynamics} drives the pursuit for a unified
model between the electronic and dielectric properties of materials.
In fact, some pioneering work\cite{Moss_1950_relation} discovered
relations between the dielectric constant $\varepsilon$ and other
physical properties, in particular the band gap $E_{\mathrm{g}}$ of bulk
semiconductors. Moss\cite{Moss_1950_relation,Moss_1985_n_Eg} showed
that $E_{\mathrm{g}}$ and $\varepsilon$ follow a semi-empirical
relation, known as the Moss relation:
\begin{equation}
\label{eq:Moss-relations}
\varepsilon^{2} E_{\mathrm{g}} \approx 95\ \mathrm{eV}
\end{equation}
Other similar semi-empirical models for the relations between
$\varepsilon$ and $E_{\mathrm{g}}$ of bulk semiconductors have also
been proposed
\cite{Ravindra_1979_eps_Eg,Ravindra_1980_model,Ravindra_2007_Eg_rev}. Despite
the minor difference between the formulae used, it is clear that there
exists certain general electronic relations in bulk
semiconductors. The existence of such general relationship is also of
high practical importance: it is generally more straightforward and
accurate to measure the band gap $E_{\mathrm{g}}$ than the static
dielectric constant $\varepsilon$, as the latter is strongly dependent
on several critical details on the sample measurements, such as
contamination, disorder, and model interpretation. With the Moss
relationship or other similar models, it is feasible to predict the
dielectric constant of a bulk semiconductor with a reasonable degree
of certainty.

While the relations between the electronic and dielectric properties
for bulk semiconductors are well-established, it is unknown if such
equation still exists in low-dimensional materials. One important
feature in atomically-thin 2D materials \cite{Novoselov_2016} is that
the electric screening is attenuated and anisotropic
\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012}. This
makes the empirical relations of dielectric constants in bulk
materials, like the Moss relation invalid within the context of 2D
materials. More critically, the static dielectric constant, a quantity
associated with the macroscopic dielectric and optoelectronic
properties and commonly obtained by theoretical calculations of 2D
materials \cite{Ramasubramaniam_2012,Wang_2016_Aip,Laturia_2018}, may
not well describe this microscopic and anisotropic dielectric nature
of 2D materials
\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Therefore, an
accurate description of the 2D dielectric nature is the prerequisite
for a 2D Moss-like relation, which could be used to make predictions
for less-investigated layered crystals and to create materials design
rules at an accurate level.  Here we show that instead of the
dielectric constant $\varepsilon$, the 2D polarizabilty $\alpha$
correctly captures the dielectric nature of a 2D material for both
in-plane and out-of-plane polarizations. Based on first principles
simulation using highly accurate hybrid functionals and quantum
mechanical models, we reveal the long-sought universal
dielectric-scale relation in the 2D world: the in-plane polarizability
$\alpha^{\parallel}$ is inversely proportional to the minimal bandgap
$E_{\mathrm{g}}$, while the out-of-plane polarizability
$\alpha^{\perp}$ is directly related with the intrinsic thickness of
2D materials. An analytical quantum-mechanical model is developed
which give a sound background to the dielectric-scale
relationships. Furthermore, such relations unify the dielectric
properties between the 2D materials and their 3D counterparts in a
natural manner, which ultimately pushes the boundary of the
understanding of electronic screening in both dimensions. The
discovery of scaling relationships between dielectric and electronic
and structural properties in 2D compounds introduces a new and general
pathway for the exploration of their complex physical and chemical
phenomena well beyond the currently possible applications.

\section{Results}
\label{sec:org752ca78}

>>>>

The central place of dielectric properties, especially the static
dielectric constant in material research
\cite{Dressel_2001_electrodynamics} drives the pursuit for a unified
model between the electronic and dielectric properties of materials.
% In fact, some pioneering work\cite{Moss_1950_relation} discovered
% relations between the dielectric constant $\varepsilon$ and other
% physical properties, in particular the band gap $E_{\mathrm{g}}$ of
% bulk semiconductors.
In fact, some pioneer
work\cite{Moss_1950_relation,Moss_1985_n_Eg,Ravindra_1979_eps_Eg,Ravindra_2007_Eg_rev}
proposed the empirical model between the energy bandgap
$E_{\mathrm{g}}$ and dielectric constant $\varepsilon$ of bulk
semiconductors, such as the famous Moss relation
\cite{Moss_1950_relation,Moss_1985_n_Eg}:
\label{eq:Moss-relations}
\varepsilon^{2} E_{\mathrm{g}} \approx 95\ \mathrm{eV}
Despite the minor difference between the empirical formulae proposed,
such general relation  is of high
practical importance for material design and engineering: with the
Moss relationship or other similar models, it is feasible to predict
the dielectric constant (and hence other parameters such as refractive
index, Bohr radius, exciton binding energy, etc.) of a bulk material
from the its bandgap with with a reasonable degree of certainty
% The
% existence of such general relationship is also of high practical
% importance: it is generally more straightforward and accurate to
% measure the band gap $E_{\mathrm{g}}$ than the static dielectric
% constant $\varepsilon$ of a bulk material, as the latter is strongly
% dependent on several critical details on the sample measurements, such
% as contamination, disorder, and model interpretation.
While the electronic-dielectric relation for bulk semiconductors is
well-established, it is unknown if such equation still exists in
atomically-thin two-dimensional (2D) materials \cite{Novoselov_2016},
due to (i) the dielectric screening of a 2D material is attenuated and
anisotropic
\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012}
and (ii) the static dielectric constant, a quantity associated with
the macroscopic dielectric and optoelectronic properties and commonly
obtained by theoretical calculations of 2D materials
\cite{Ramasubramaniam_2012,Wang_2016_Aip,Laturia_2018}, may not well
describe this microscopic and anisotropic dielectric nature of 2D
materials \cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}.
% Therefore, an
% accurate description of the 2D dielectric nature is the prerequisite
% for a 2D Moss-like relation, which could be used to make predictions
% for less-investigated layered crystals and to create materials design
% rules at an accurate level.
Here we show that instead of the dielectric constant $\varepsilon$,
the 2D polarizabilty $\alpha$ correctly captures the dielectric nature
of a 2D material. Based on both theoretical model and first principle
calculations, we reveal the long-sought universal dielectric scaling
relations for 2D materials, depend both on the electronic and
structural information: the in-plane polarizability
$\alpha^{\parallel}$ is inversely proportional to the minimal bandgap
$E_{\mathrm{g}}$, while the out-of-plane polarizability
$\alpha^{\perp}$ is directly related with the intrinsic thickness of
2D materials. We further introduce the concept of dielectric
anisotropy index, to unify 2D and 3D dielectric property. The proposed
universal dielectric scaling relationships of 2D compounds introduce a
general pathway for the exploration of their complex physical and
chemical phenomena well beyond the currently possible applications.
% Based on this
% framework, we further unify the concept of dielectric properties of
% any material dimension, by the dielectric anisotropy index, 
% An analytical quantum-mechanical model is developed
% which give a sound background to the dielectric-scale
% relationships.
% Using such unified relations unify the dielectric
% properties between the 2D materials and their 3D counterparts in a
% natural manner, which ultimately pushes the boundary of the
% understanding of electronic screening in both dimensions.
% The discovery of scaling relationships between dielectric and electronic
% and structural properties in 2D compounds introduces a new and general
% pathway for the exploration of their complex physical and chemical
% phenomena well beyond the currently possible applications.

% \section{Results}
% \label{sec:org752ca78}
